---
title: "Dirty Data Project Task 3"
output: html_notebook
---

# Introduction

The data used in this task comes from 2 data sets - bird data and ship data.

The bird data contains information about individual sightings of birds, for
example, the species name, age, sex, count, etc.

The ship data contains information about location, sea, weather conditions, etc.

# Cleaning Process

For each data set, I cleaned the column names and then selected only the columns
that are needed for analysis. 

```{r}
ship_data <- raw_ship_data %>% 
  janitor::clean_names() %>% 
  select(record_id, lat, long)
```

I also removed the data where no bird sightings were recorded, as I am only 
interested in the sightings.

```{r}
bird_data <- raw_bird_data %>% 
  janitor::clean_names() %>% 
  rename_with(str_remove, pattern = "_taxon_age_sex_plumage_phase") %>% 
  select(record_id, species_common_name, species_scientific_name, 
         species_abbreviation, count) %>% 
  filter(species_common_name != "[NO BIRDS RECORDED]")
```

Finally, I used `left_join()` to join the 2 data sets together and unselected 
the column record_id. 

```{r}
all_data <- bird_data %>% 
  left_join(ship_data, by = "record_id") %>% 
  select(-record_id)
```

# Analysis Answers

**1. Which bird had the most individual sightings?**

The "Wandering albatross sensu lato PL2, *Diomedea antipodensis / exulans PL2*, 
DIOANTEXU PL2" had the most individual sightings - 3104.

**2. Which bird had the highest total count?**

The "Short-tailed shearwater, *Puffinus tenuirostris*, PUFTEN" had the highest 
total count - 982,553.

**3. Which bird had the highest total count above a latitude of -30?**

Wedge-tailed shearwater, *Puffinus pacificus*, PUFPAC - 29

**4. How many different types of birds were only ever seen in groups of 1?**

There were 86 types of birds that were ever observed in groups of 1

**5. How many penguins were seen? (Hint: there are many types of penguin)**

There were 154 penguins seen in total.