---
title: "Dirty Data Project - Task 2"
output: html_notebook
---

# Introduction 

The data used in this task consists of 18 different cakes and the amount of
ingredients used for each cake. There is also a data set containing the 
long form of all the ingredient names, as well as the measurement type for each
ingredient.

# Assumptions

I assumed that all missing values represent ingredients that are not used in
a cake, and there are no missing values for ingredients that are present.

# Cleaning Process

I cleaned the column names and pivoted the tibble for a more clear layout. 

```{r}
cake_data_pivoted <- raw_cake_data %>% 
  rename("cake" = "Cake") %>% 
  pivot_longer(-cake, names_to = "ingredients_code", values_to = "amount")
```

There was one instance of 2 values being present in one cell, I used 
`str_replace()` and `coalesce()` to move the information to the correct column.

I then joined the code to the main data using `left_join()`.

Finally, I filtered out all NAs from the "amount" column based on my 
assumptions.

```{r}
# I dropped the ingredient code column and removed NAs, because I am only 
# interested in ingredients that are used for each cake.
clean_cake_data <- cake_data_joined %>% 
  select(cake, ingredient, amount, measure) %>% 
  filter(!is.na(amount))
```

# Analysis Answers

**1. Which cake has the most cocoa in it?**

One Bowl Chocolate cake has the most cocoa in it - 10 tablespoons. 

**2. For sponge cake, how many cups of ingredients are used in total?**

In total, 3.5 cups of ingredients are used for sponge cake. 

**3. How many ingredients are measured in teaspoons?**

There are a total of 8 ingredients in this data set that are measured in 
teaspoons.

**4. Which cake has the most unique ingredients?**

There are 2 cakes, "Babas au Rhum" and "One Bowl Chocolate" that both use 11 
unique ingredients, which is the most in this data set.

**5. Which ingredients are used only once?**

There are 8 ingredients that are used only once. They are: Bananas, 
Cream of tartar, Crushed Ice, Dried currants, Egg white, Nutmeg, Nuts and
Zwiebach.
