---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
all_candy_data <- read_csv("clean_data/all_candy_data.csv")
```


What is the total number of candy ratings given across the three years. 

```{r}
all_candy_data %>% 
  summarise(num_ratings = sum(!is.na(rating)))
```


What was the average age of people who are going out trick or treating and the 
average age of people not going trick or treating?

```{r}
all_candy_data %>% 
  filter(!is.na(going_out)) %>% 
  group_by(going_out) %>% 
  summarise(avg_age = mean(age, na.rm = TRUE))
```


For each of joy, despair and meh, which candy bar received the most of 
these ratings?

```{r}
all_candy_data %>%
  filter(!is.na(rating)) %>% 
  group_by(candy_name, rating) %>% 
  summarise(num_ratings = n()) %>%
  ungroup() %>% 
  group_by(rating) %>% 
  slice_max(num_ratings, n = 1)
```


How many people rated Starburst as despair?

```{r}
all_candy_data %>% 
  filter(candy_name == "starburst" & rating == "DESPAIR") %>% 
  summarise(num_ratings = n())
```


For the next three questions, count despair as -1, joy as +1 and meh as 0.

```{r}
all_candy_data_numeric_rating <- all_candy_data %>% 
  mutate(rating = case_when(
    rating == "JOY" ~ +1,
    rating == "MEH" ~ 0,
    rating == "DESPAIR" ~ -1
  ))
```


What was the most popular candy bar by this rating system for each gender 
in the dataset?

```{r}
all_candy_data_numeric_rating %>% 
  filter(!is.na(gender)) %>% 
  group_by(gender, candy_name) %>% 
  summarise(rating = sum(rating, na.rm = TRUE)) %>% 
  slice_max(rating, n = 1)
```


What was the most popular candy bar in each year?

```{r}
all_candy_data_numeric_rating %>% 
  group_by(year, candy_name) %>% 
  summarise(rating = sum(rating, na.rm = TRUE)) %>% 
  slice_max(rating, n = 1)
```


What was the most popular candy bar by this rating for people in US, Canada, UK and all other countries?

```{r}
all_candy_data_numeric_rating %>% 
  filter(!is.na(country)) %>% 
  group_by(country, candy_name) %>% 
  summarise(rating = sum(rating, na.rm = TRUE)) %>% 
  slice_max(rating, n = 1, with_ties = FALSE)
```

```{r}
all_candy_data_numeric_rating %>% 
  mutate(country = if_else(country == "United States of America" | 
                             country == "Canada" |
                             country == "United Kingdom",
                           country,
                           "Other"
                           )) %>% 
  filter(!is.na(country)) %>% 
  group_by(country, candy_name) %>% 
  summarise(rating = sum(rating, na.rm = TRUE)) %>% 
  slice_max(rating, n = 1)
```

