---
title: "Dirty Data Project - Task 4"
output: html_notebook
---

# Introduction

For this task, I have used 3 data sets on halloween candy ratings, gathered 
using a survey. 

Each data set includes answers to a set of personal questions,
such as age, gender, country etc. The next part of the survey asks people to 
rate halloween candy, using ratings "JOY", "MEH" and "DESPAIR". Lastly there are 
a final set of columns with additional comments, ratings etc.

The 3 data sets represent candy ratings from 3 different years - 2015, 2016
and 2017.

A few things to note:

* There are types of candy that do not appear in every data set.

* 2015 data does not include gender or location.

# Assumptions

Age cannot be higher than 125 years.

# Cleaning Process

The first thing I did was clean column names using the janitor package. Then, I 
dropped the columns at the end of each data set that included extra comments and
unrelated ratings and questions.

I then removed all columns from the data that I did not need for my analysis.
These included the columns timestamp and state/province, as well as things such 
as medicine, money, DVDs and other foods that are not candy.

I added a year column for each of the data sets, so as to not lose that data 
once combined.

I joined the data sets using `bind_rows()` and then cleaned up columns gender,
age and country.

```{r}
all_candy_data_fix_gender <- all_candy_data_fix_going_out %>% 
  mutate(gender = na_if(gender, "I'd rather not say"))
```

```{r}
all_candy_data_fix_age <- all_candy_data_fix_gender %>% 
  mutate(age = as.numeric(age),
         age = if_else(age > 125,
                       NaN,
                       age))
```

For the country column, I used `case_when()` to turn all invalid answers to NAs
and `str_replace()` to fix typos etc.

Finally, I pivoted the tibble into a long format. 

```{r}
all_candy_data_pivoted <- all_candy_data_fix_country %>% 
  pivot_longer(x100_grand_bar:peanut_butter_bars,
               names_to = "candy_name", 
               values_to = "rating")
```

# Analysis Answers

**1. What is the total number of candy ratings given across the three years. 
(number of candy ratings, not number of raters. Don’t count missing values)**

The total number of ratings is 605,174.

**2. What was the average age of people who are going out trick or treating and 
the average age of people not going trick or treating?**

The average age of people that are going out is 35 and the average age of people 
not going trick or treating is 39.

***3. For each of joy, despair and meh, which candy bar received the most of 
these ratings?**

The candy that received the most "joy" (7589) is "Any full sized candy bar". 
Most "meh" (1570) went to Lollipops and most "despair" (7341) to 
"Gum from baseball cards". 

**4. How many people rated Starburst as despair?**

A total of 1990 people rated Starburst as "despair".

**For the next three questions, count despair as -1, joy as +1 and meh as 0.**

**5. What was the most popular candy bar by this rating system for each gender 
in the dataset?**

"Any full sized candy bar" was the most popular among everyone - males, females 
and other.

**6. What was the most popular candy bar in each year?**

Every year "Any full sized candy bar" was the most popular.

**7. What was the most popular candy bar by this rating for people in US, 
Canada, UK and all other countries?**

The most popular candy in USA, Canada and other countries was "Any full sized 
candy bar". In the Uk however, there was a four-way tie between "Any full sized
candy bar", Lindt truffle, Rolos and Toblerone.

